Feeding Dynamic Behavior into Optimization: Simulation-based Multi-objective Overtime Planning

### 2014-08-30 data/result/Article/Latex/Article.tex
Publicação do número de dependências no cronograma

\noindent
\textbf{Representation}. A candidate solution for OPP is a sequence of m integer numbers, m being the number of activities. Each number in the solution pertains to the [0..8] integer interval and represents a multiple of 30-minutes overtime for a given activity. Thus, if the number 4 is assigned to activity A, A will receive 1.5 hours of overtime work. Each individual solution being evolved by NSGAII is evaluated through simulation. The simulator activates the overtime scenario upon each activity in the schedule according to the number of overtime hours assigned to that activity in the solution. Then, the simulator calculates the number of overtime hours, project makespan, and project cost for that solution.

@@

\noindent
\textbf{Mutation}. As in Ferrucci et al. \cite{Ferrucci:2013}, mutations are executed for all crossover offspring. Each gene of an offspring O is changed with 30\% probability, being assigned a new value in the [0..8] integer interval.

@@

Table I presents information about the selected instances for the experimental analysis. The {\it Transaction Functions} and {\it Data Functions} columns count, respectively, the number of transaction and data functions for each instance. These values are related to the number of function points of the instance, presented in the last column. The {\it Work Packages} column presents the number of groups on which the data and transaction functions distributed to form the project schedule.

% Table generated by Excel2LaTeX from sheet 'tabela 1'
\begin{table}[htbp]
  \centering
  \caption{Instances used in the experimental studies}
    \begin{tabular}
		{
			p{0.7cm} 
			>{\centering\arraybackslash}p{1.5cm} 
			>{\centering\arraybackslash}p{1.3cm} 
			>{\centering\arraybackslash}p{1.3cm} 
			>{\centering\arraybackslash}p{1.3cm}
		}
    \toprule
		Name & Transaction Functions & Data Functions & Work Packages & Function Points \\
    \midrule
    ACAD  & 39    & 7     & 10    & 185 \\
    WMET  & 48    & 7     & 11    & 225 \\
    WAMS  & 67    & 8     & 15    & 381 \\
    PSOA  & 65    & 9     & 18    & 290 \\
    OMET  & 129   & 22    & 21    & 635 \\
    PARM  & 98    & 21    & 27    & 451 \\
    \bottomrule
    \end{tabular}%
\end{table}%

>>>>

\noindent
\textbf{Representation}. A candidate solution for OPP is a sequence of m integer numbers, m being the number of activities. Each number in the solution pertains to the [0, 8] integer interval and represents a multiple of 30-minutes overtime for a given activity. Thus, if the number 4 is assigned to activity A, A will receive 1.5 hours of overtime work. Each individual solution being evolved by NSGAII is evaluated through simulation. The simulator activates the overtime scenario upon each activity in the schedule according to the number of overtime hours assigned to that activity in the solution. Then, the simulator calculates the number of overtime hours, project makespan, and project cost for that solution.

@@

\noindent
\textbf{Mutation}. Mutations are executed for all crossover offspring. Each gene of an offspring O is changed with 30\% probability, being assigned a new value in the [0, 8] integer interval.

@@

Table I presents information about the selected instances for the experimental analysis. The {\it TF} and {\it DF} columns count, respectively, the number of transaction and data functions for each instance. These values are related to the number of function points of the instance, presented in the last column ({\it FP}). The {\it WP} column presents the number of groups on which the data and transaction functions were distributed to form the project schedule, the {\it ACT} column shows the number of activities in the schedule and the {\it DEP} column shows the number of dependencies among these activities.

% Table generated by Excel2LaTeX from sheet 'tabela 1'
\begin{table}[htbp]
  \centering
  \caption{Instances used in the experimental studies}
    \begin{tabular}
		{lcccccc
%			p{0.7cm} 
%			>{\centering\arraybackslash}p{1.5cm} 
%			>{\centering\arraybackslash}p{1.3cm} 
%			>{\centering\arraybackslash}p{1.3cm} 
%			>{\centering\arraybackslash}p{1.3cm}
		}
    \toprule
		Name & TF & DF & WP & ACT & DEP & FP \\
    \midrule
    ACAD  & 39    & 7     & 10    &  40  &  39  & 185 \\
    WMET  & 48    & 7     & 11    &  44  &  33  & 225 \\
    WAMS  & 67    & 8     & 15    &  60  &  45  & 381 \\
    PSOA  & 65    & 9     & 18    &  72  &  84  & 290 \\
    OMET  & 129   & 22    & 21    &  84  &  63  & 635 \\
    PARM  & 98    & 21    & 27    & 108  &  91  & 451 \\
    \bottomrule
    \end{tabular}%
\end{table}%
